---
title: "Cod"
output: html_document
date: "2024-07-17"
---


```{r}
library(dplyr)
library(ggplot2)

load("C:/Users/lucab/Downloads/stomach_dataset.Rdata") 

sprat <- stom_df%>%filter(pred_taxa=="Gadus morhua")

```

```{r}

ggplot(sprat, aes(x=pred_weight_g, y=log(ppmr)))+
  geom_point()+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")

```


```{r}
dig <- 1

ggplot(sprat, aes(x=pred_weight_g, y=log(ppmr)))+
  geom_point()+
  facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*sprat$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")


```

 The PPMR does seem to increase at the largest sizes, should I remove or just
 ignore?
 
```{r}

sprat$weight_numbers <- sprat$nprey_perpred
sprat$weight_biomass <- sprat$nprey_perpred*sprat$prey_ind_weight_g^dig

ggplot() +
  geom_density(data = sprat, aes(x = log(ppmr), weight = weight_biomass), color = "red") +
  geom_density(data = sprat, aes(x = log(ppmr), weight = weight_numbers), color = "blue") +
  labs(title = "Density Plot of log(ppmr) Weighted by Biomass and Numbers",
       x = "log(ppmr)",
       y = "Density") +
  theme_minimal()


```   



```{r}

sprat <- sprat%>%filter(nprey_perpred>0)

library(mclust)

repeat_elements <- function(data, weights) {

  valid_indices <- !is.na(data) & !is.na(weights)
  data <- data[valid_indices]
  weights <- weights[valid_indices]
  
  final_vector <- c()

  for (i in seq_along(data)) {

    rounded_weight <- round(weights[i])

    repeated_values <- rep(data[i], times = rounded_weight)

    final_vector <- c(final_vector, repeated_values)
  }
  
  return(final_vector)
}

spratnu <- repeat_elements(log(sprat$ppmr), sprat$nprey_perpred)

gmm <- densityMclust(spratnu, G=1)

```

```{r}

dplot <- data.frame(x=gmm[["data"]], density=gmm[["density"]])


(numbfit <- ggplot() +
    geom_density(data=sprat, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
  geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Number Density Plot from Number Distribution"))

```

Ok this gaussian fits nicely, does it shift?

```{r}

newspratdens <- gmm[["density"]]*exp(-dig*gmm[["data"]])
shifted_pdf_normalized <- newspratdens / sum(newspratdens) 

#making new dataframe
dplot <- data.frame(x=gmm[["data"]], density=shifted_pdf_normalized)

(numbfitbio <- ggplot() +
    geom_density(data=sprat, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
    geom_density(data=dplot, aes(x, weight=shifted_pdf_normalized), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

```

This isnt the best shift, lets try to shift it the other way.

```{r}

stomach <- sprat

haddocknu <- repeat_elements(log(stomach$ppmr), stomach$nprey_perpred*
                               stomach$prey_ind_weight_g^dig)
gmm <- densityMclust(haddocknu, G=1)


dplot <- data.frame(x=gmm[["data"]], density=gmm[["density"]])

(biofit <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
  geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Diet Distribution"))

shifted_fit <- gmm
shifted_fit[["parameters"]][["mean"]] <- shifted_fit[["parameters"]][["mean"]]+
  (2/3)*shifted_fit[["parameters"]][["variance"]][["sigmasq"]]

stomach <- stomach%>%filter(!is.na(ppmr))

x_vals <- seq(min(log(stomach$ppmr)), max(log(stomach$ppmr)), length.out = 1000)

#generating the density values 
shifted_pdf <- sapply(x_vals, function(x) {
  sum(shifted_fit$parameters$pro * dnorm(x, mean = shifted_fit$parameters$mean, sd = sqrt(shifted_fit$parameters$variance$sigmasq)))
})

plot_data <- data.frame(x = x_vals, shifted_pdf = shifted_pdf)


(numbfitbio <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
    geom_density(data=plot_data, aes(x, weight=shifted_pdf), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

#different way

newspratdens <- gmm[["density"]]*exp(dig*gmm[["data"]])

shifted_pdf_normalized <- newspratdens / sum(newspratdens) 

dplot <- data.frame(x=gmm[["data"]], density=shifted_pdf_normalized)

(numbfitbio <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
    geom_density(data=dplot, aes(x, weight=shifted_pdf_normalized), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

```


Okay, it doesn't shift well either here. I will try the exponential.


```{r}

fl <- function(l, alpha, ll, ul, lr, ur) {
  dl <- ll - l
  dr <- l - lr
  fl_values <- exp(alpha * l) / (1 + exp(ul * dl)) / (1 + exp(ur * dr))
  
  # Debugging output
  if (any(!is.finite(fl_values))) {
    print("Non-finite fl values found")
    print(fl_values)
  }
  
  return(fl_values)
}

## Define the truncated exponential PDF with debugging
dtexp <- function(l, alpha, ll, ul, lr, ur) {
  fl_values <- fl(l, alpha, ll, ul, lr, ur)
  
  integral_result <- tryCatch(
    integrate(fl, 0, 30, alpha = alpha, ll = ll, ul = ul, lr = lr, ur = ur),
    error = function(e) {
      print("Integration failed")
     print(e)
      return(NULL)
    }
   )
   
   if (is.null(integral_result)) {
     return(rep(NA, length(l)))
   }
   
   d <- fl_values / integral_result$value
   
  # Debugging output
  if (any(!is.finite(d))) {
    print("Non-finite d values found")
    print(d)
  }
  
  return(d)
}

 #Define the MLE function with debugging
mle_texp <- function(df) {
  loglik <- function(alpha, ll, ul, lr, ur) {
    L <- dtexp(df$l, alpha, ll, ul, lr, ur)
    
    # Debugging output
    if (any(!is.finite(L) | L <= 0)) {
     print("Non-finite or non-positive L values found")
      print(which(!is.finite(L) | L <= 0))
      return(Inf)
    }
    
    -sum(log(L) * df$weight_numbers)
  }
  
  result <- tryCatch(
    mle2(loglik, start = list(
      alpha = 0.5,
      ll = min(df$l),
      lr = max(df$l),
      ul = 5,
      ur = 5
    ), method = "L-BFGS-B", control = list(maxit = 10000)),
    error = function(e) {
      print("MLE fitting failed")
      print(e)
      return(NULL)
    }
  )
  
  return(result)
}


```

```{r}
library(bbmle)

stomach <- stomach%>%mutate(l=log(ppmr))%>%filter(!is.na(l))


est <- mle_texp(stomach)

biomassco <- est@coef

grid = seq(min(stomach$l), max(stomach$l), length.out = 200)

dist <- dtexp(grid, alpha = (biomassco[1]), ll = biomassco[2], ul = biomassco[3], 
              lr = biomassco[4], ur = biomassco[5])

dist <- data.frame(l=grid, Density=dist)

  ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = dist, color = "red")

```

Fits okay, does it shift.

```{r}
numberestco <- biomassco

dist <- dtexp(grid, alpha = (numberestco[1]), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
numberdist <- data.frame(l=grid, Density=dist)
dist <- dtexp(grid, alpha = (numberestco[1]-2/3), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
biomassdist <- data.frame(l=grid, Density=dist)
#now plot these two together

stomach <- stomach %>% mutate(biomass = nprey_perpred * prey_ind_weight_g)

ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = biomassdist, color = "red")+
  geom_line(aes(l, Density), data = numberdist, color = "blue")+
  xlim(0,13)

```

This doesn't fit well. Its okay, but it is still off.

Will try it the other way around and compare. (fitting number from diet)


```{r}

stomach <- stomach%>%mutate(weight_numbers=nprey_perpred*stomach$prey_ind_weight_g^dig)

est <- mle_texp(stomach)

estco <- est@fullcoef
grid = seq(0, 30, length.out = 200)
dist <- dtexp(grid, alpha = estco[1], ll = estco[2], ul = estco[3], lr = estco[4], ur = estco[5])
dist <- data.frame(l=grid, Density=dist)

ggplot(stomach) + 
  geom_density(aes(l, weight=nprey_perpred*stomach$prey_ind_weight_g^dig))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = dist, color = "red")


```

```{r}

dist <- dtexp(grid, alpha = estco[1]+2/3, ll = estco[2], ul = estco[3], lr = estco[4], ur = estco[5])
dist <- data.frame(l=grid, Density=dist)

ggplot(stomach) + 
  geom_density(aes(l, weight=nprey_perpred))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = dist, color = "red")

```

It doesnt fit well for both.

But shifting across number to diet works the best I think.