 b---
title: "Haddock"
output: html_document
date: "2024-07-15"
---
```{r}
library(dplyr)
library(ggplot2)

load("C:/Users/lucab/Downloads/stomach_dataset.Rdata") 

haddock <- stom_df%>%filter(pred_taxa=="Melanogrammus aeglefinus")

```

```{r}

#whiting <- whiting%>%filter(pred_weight_g<10000, nprey_perpred > 1)

ggplot(haddock, aes(x=log(pred_weight_g), y=log(ppmr)))+
  geom_point()+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")

```

```{r}
dig <- 2/3

ggplot(haddock, aes(x=(pred_weight_g), y=log(ppmr)))+
  geom_point()+
  #facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*haddock$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")


```

Once it is weighted by biomass, it works, but the PPMR still decreases
at larger sizes. I think it should still be okay.

```{r}

stomach <- haddock
stomach$weight_numbers <- stomach$nprey_perpred
stomach$weight_biomass <- stomach$nprey_perpred*stomach$prey_ind_weight_g^dig

ggplot() +
  geom_density(data = stomach, aes(x = log(ppmr), weight = weight_biomass), color = "red") +
  geom_density(data = stomach, aes(x = log(ppmr), weight = weight_numbers), color = "blue") +
  labs(title = "Density Plot of log(ppmr) Weighted by Biomass and Numbers",
       x = "log(ppmr)",
       y = "Density") +
  theme_minimal()

````

I think that a mixture gaussian model would fit this best.

```{r}


library(mclust)

repeat_elements <- function(data, weights) {

    valid_indices <- !is.na(data) & !is.na(weights)
  data <- data[valid_indices]
  weights <- weights[valid_indices]
  
  final_vector <- c()

  for (i in seq_along(data)) {

    rounded_weight <- round(weights[i])

    repeated_values <- rep(data[i], times = rounded_weight)

    final_vector <- c(final_vector, repeated_values)
  }
  
  return(final_vector)
}

haddocknu <- repeat_elements(log(stomach$ppmr), stomach$nprey_perpred)

gmm <- densityMclust(haddocknu, G=3)


```

This isnt the best fit, it missses out a peak at higher PPMR. When it is run 
with 3 gaussians, the 3rd peak has an extremely high density, which makes me 
think that there is something wrong with the data here. If it didnt have such 
a high density it would fit it very well.

I want to see if I filter out this data it would work better, or if this 
data is from the same year/region.

```{r}

ggplot(stomach, aes(x=log(ppmr), y=nprey_perpred))+
  geom_point()+
  labs(title="PPMR vs Prey Individual Weight", x="PPMR", y="Prey Individual Weight")

```


Ok, so there are two datapoints with a very high nprey per pred, so this means
that it skews the distribution, I want to remove it and rerun the fit.

```{r}

stomach <- stomach%>%filter(nprey_perpred<2000)
haddocknu <- repeat_elements(log(stomach$ppmr), stomach$nprey_perpred)
gmm <- densityMclust(haddocknu, G=2)

```


This looks to be a good fit. Lets see if it shifts!

```{r}

dplot <- data.frame(x=gmm[["data"]], density=gmm[["density"]])

(biofit <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
  geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Diet Distribution"))

shifted_fit <- gmm
shifted_fit[["parameters"]][["mean"]] <- shifted_fit[["parameters"]][["mean"]]-
  (2/3)*shifted_fit[["parameters"]][["variance"]][["sigmasq"]]

stomach <- stomach%>%filter(!is.na(ppmr))

x_vals <- seq(min(log(stomach$ppmr)), max(log(stomach$ppmr)), length.out = 1000)

#generating the density values 
shifted_pdf <- sapply(x_vals, function(x) {
  sum(shifted_fit$parameters$pro * dnorm(x, mean = shifted_fit$parameters$mean, sd = sqrt(shifted_fit$parameters$variance$sigmasq)))
})

plot_data <- data.frame(x = x_vals, shifted_pdf = shifted_pdf)


(numbfitbio <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
    geom_density(data=plot_data, aes(x, weight=shifted_pdf), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

#doing it in a different way

newspratdens <- gmm[["density"]]*exp(-dig*gmm[["data"]])

shifted_pdf_normalized <- newspratdens / sum(newspratdens) 

dplot <- data.frame(x=gmm[["data"]], density=shifted_pdf_normalized)

(numbfitbio <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
    geom_density(data=dplot, aes(x, weight=shifted_pdf_normalized), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))


```

Ok, so it doesn't shift, will have to try biomass to number

```{r}

haddocknu <- repeat_elements(log(stomach$ppmr), stomach$nprey_perpred*
                               stomach$prey_ind_weight_g^dig)
gmm <- densityMclust(haddocknu, G=2)


dplot <- data.frame(x=gmm[["data"]], density=gmm[["density"]])

(biofit <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
  geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Diet Distribution"))

shifted_fit <- gmm
shifted_fit[["parameters"]][["mean"]] <- shifted_fit[["parameters"]][["mean"]]+
  (2/3)*shifted_fit[["parameters"]][["variance"]][["sigmasq"]]

stomach <- stomach%>%filter(!is.na(ppmr))

x_vals <- seq(min(log(stomach$ppmr)), max(log(stomach$ppmr)), length.out = 1000)

#generating the density values 
shifted_pdf <- sapply(x_vals, function(x) {
  sum(shifted_fit$parameters$pro * dnorm(x, mean = shifted_fit$parameters$mean, sd = sqrt(shifted_fit$parameters$variance$sigmasq)))
})

plot_data <- data.frame(x = x_vals, shifted_pdf = shifted_pdf)


(numbfitbio <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
    geom_density(data=plot_data, aes(x, weight=shifted_pdf), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

#different way

newspratdens <- gmm[["density"]]*exp(dig*gmm[["data"]])

shifted_pdf_normalized <- newspratdens / sum(newspratdens) 

dplot <- data.frame(x=gmm[["data"]], density=shifted_pdf_normalized)

(numbfitbio <- ggplot() +
    geom_density(data=stomach, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
    geom_density(data=dplot, aes(x, weight=shifted_pdf_normalized), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

```

Its better, but I still dont think its good enough, the mixture % do not 
change. As neither of them shift, I think I am going to have to fit
the exponential, and see if that shifts.


```{r}

fl <- function(l, alpha, ll, ul, lr, ur) {
  dl <- ll - l
  dr <- l - lr
  fl_values <- exp(alpha * l) / (1 + exp(ul * dl)) / (1 + exp(ur * dr))
  
  # Debugging output
  if (any(!is.finite(fl_values))) {
    print("Non-finite fl values found")
    print(fl_values)
  }
  
  return(fl_values)
}

## Define the truncated exponential PDF with debugging
dtexp <- function(l, alpha, ll, ul, lr, ur) {
  fl_values <- fl(l, alpha, ll, ul, lr, ur)
  
  integral_result <- tryCatch(
    integrate(fl, 0, 30, alpha = alpha, ll = ll, ul = ul, lr = lr, ur = ur),
    error = function(e) {
      print("Integration failed")
     print(e)
      return(NULL)
    }
   )
   
   if (is.null(integral_result)) {
     return(rep(NA, length(l)))
   }
   
   d <- fl_values / integral_result$value
   
  # Debugging output
  if (any(!is.finite(d))) {
    print("Non-finite d values found")
    print(d)
  }
  
  return(d)
}

 #Define the MLE function with debugging
mle_texp <- function(df) {
  loglik <- function(alpha, ll, ul, lr, ur) {
    L <- dtexp(df$l, alpha, ll, ul, lr, ur)
    
    # Debugging output
    if (any(!is.finite(L) | L <= 0)) {
     print("Non-finite or non-positive L values found")
      print(which(!is.finite(L) | L <= 0))
      return(Inf)
    }
    
    -sum(log(L) * df$weight_numbers)
  }
  
  result <- tryCatch(
    mle2(loglik, start = list(
      alpha = 0.5,
      ll = min(df$l),
      lr = max(df$l),
      ul = 5,
      ur = 5
    ), method = "L-BFGS-B", control = list(maxit = 10000)),
    error = function(e) {
      print("MLE fitting failed")
      print(e)
      return(NULL)
    }
  )
  
  return(result)
}


```

```{r}
library(bbmle)

stomach <- stomach%>%mutate(l=log(ppmr))

est <- mle_texp(stomach)

biomassco <- est@coef

grid = seq(0, 30, length.out = 200)
#here, the alpha is meant to be -1, but I have to subtract 0.7 to make it work, so I am going to run the distribution again
#for the biomass, and see the difference
dist <- dtexp(grid, alpha = (biomassco[1]), ll = biomassco[2], ul = biomassco[3], 
              lr = biomassco[4], ur = biomassco[5])

dist <- data.frame(l=grid, Density=dist)

  ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = dist, color = "red")

```

Ok the exponential fits well, now lets shift!


```{r}
numberestco <- biomassco

dist <- dtexp(grid, alpha = (numberestco[1]), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
numberdist <- data.frame(l=grid, Density=dist)
dist <- dtexp(grid, alpha = (numberestco[1]-0.625), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
biomassdist <- data.frame(l=grid, Density=dist)
#now plot these two together

stomach <- stomach %>% mutate(biomass = nprey_perpred * prey_ind_weight_g^(2/3))

ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = biomassdist, color = "red")+
  geom_line(aes(l, Density), data = numberdist, color = "blue")

```

This fits well. 

     alpha         ll         ul         lr         ur 
 0.4805395  3.8865861  2.1827656 11.7890770  2.3939047 
 
 Does fitting to biomass and shifting mean a better fit?
 
 
```{r}


stomach <- stomach%>%mutate(l=log(ppmr))

stomach <- stomach%>%mutate(weight_numbers = stomach$nprey_perpred*
                              stomach$prey_ind_weight_g^dig)

est <- mle_texp(stomach)

biomassco <- est@coef

grid = seq(0, 30, length.out = 200)
#here, the alpha is meant to be -1, but I have to subtract 0.7 to make it work, so I am going to run the distribution again
#for the biomass, and see the difference
dist <- dtexp(grid, alpha = (biomassco[1]), ll = biomassco[2], ul = biomassco[3], 
              lr = biomassco[4], ur = biomassco[5])

dist <- data.frame(l=grid, Density=dist)

  ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = dist, color = "red")

numberestco <- biomassco

dist <- dtexp(grid, alpha = (numberestco[1]), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
numberdist <- data.frame(l=grid, Density=dist)
dist <- dtexp(grid, alpha = (numberestco[1]+0.625), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
biomassdist <- data.frame(l=grid, Density=dist)
#now plot these two together

stomach <- stomach %>% mutate(biomass = nprey_perpred)

ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = biomassdist, color = "red")+
  geom_line(aes(l, Density), data = numberdist, color = "blue")
  
```

They are both the same - both underestimate either number or biomass.

However, for it to be better modelled by the exponential, when it is not a filter
feeder is strange. It does seem that there are 2 feeding modes, but the 
mixture gaussian model does not shift between biomass and number distributions
well even thought ecologically it should be modelled by this.