---
title: "Haddock"
output: html_document
date: "2024-07-15"
---
```{r}
library(dplyr)
library(ggplot2)

load("C:/Users/lucab/Downloads/stomach_dataset.Rdata") 

haddock <- stom_df%>%filter(pred_taxa=="Melanogrammus aeglefinus")

```

```{r}

#whiting <- whiting%>%filter(pred_weight_g<10000, nprey_perpred > 1)

ggplot(haddock, aes(x=log(pred_weight_g), y=log(ppmr)))+
  geom_point()+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")

```

```{r}
dig <- 2/3

ggplot(haddock, aes(x=(pred_weight_g), y=log(ppmr)))+
  geom_point()+
  #facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*haddock$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")


```

Once it is weighted by biomass, it works, but the PPMR still decreases
at larger sizes. I think it should still be okay.

```{r}

stomach <- haddock
stomach$weight_numbers <- stomach$nprey_perpred
stomach$weight_biomass <- stomach$nprey_perpred*stomach$prey_ind_weight_g^dig

ggplot() +
  geom_density(data = stomach, aes(x = log(ppmr), weight = weight_biomass), color = "red") +
  geom_density(data = stomach, aes(x = log(ppmr), weight = weight_numbers), color = "blue") +
  labs(title = "Density Plot of log(ppmr) Weighted by Biomass and Numbers",
       x = "log(ppmr)",
       y = "Density") +
  theme_minimal()

````

I think that a mixture gaussian model would fit this best.

```{r}


library(mclust)

repeat_elements <- function(data, weights) {

    valid_indices <- !is.na(data) & !is.na(weights)
  data <- data[valid_indices]
  weights <- weights[valid_indices]
  
  final_vector <- c()

  for (i in seq_along(data)) {

    rounded_weight <- round(weights[i])

    repeated_values <- rep(data[i], times = rounded_weight)

    final_vector <- c(final_vector, repeated_values)
  }
  
  return(final_vector)
}

haddocknu <- repeat_elements(log(stomach$ppmr), stomach$nprey_perpred)

gmm <- densityMclust(haddocknu, G=3)


```

This isnt the best fit, it missses out a peak at higher PPMR. When it is run 
with 3 gaussians, the 3rd peak has an extremely high density, which makes me 
think that there is something wrong with the data here. If it didnt have such 
a high density it would fit it very well.

I want to see if I filter out this data it would work better, or if this 
data is from the same year/region.