---
title: "Herring"
output:
  pdf_document: default
  html_document: default
date: "2024-07-21"
---


```{r}
library(dplyr)
library(ggplot2)
library(bbmle)
load("C:/Users/lucab/Downloads/stomach_dataset.Rdata") 

sprat <- stom_df%>%filter(pred_taxa=="Clupea harengus")

```

```{r}

ggplot(sprat, aes(x=pred_weight_g, y=log(ppmr)))+
  geom_point()+
  facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")

```

Even though all this data is from dapstom, there appears to be 2 different 
sources, there are 2 groups in the points. I will also remove this pred weight
outlier point, and also change biomass



```{r}
dig <- 1

sprat <- sprat%>%filter(pred_weight_g<1000)

ggplot(sprat, aes(x=pred_weight_g, y=log(ppmr)))+
  geom_point()+
  facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*sprat$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")


```

THere are definitely two groups.

```{r}

ggplot(sprat, aes(x=pred_weight_g, y=log(ppmr), color=year))+
  geom_point()+
  facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*sprat$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")


```

There are a lot of the smallest points that are from 1900, and are grouped 
weights.I will plot just from 2000 and see how it is.

```{r}

sprat2 <- sprat%>%filter(year>2000)

ggplot(sprat2, aes(x=pred_weight_g, y=log(ppmr)))+
  geom_point()+
  facet_wrap(~data)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*sprat2$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")


```

No, it still increases, what if I plot both groups.

```{r}

sprat2 <- sprat2%>%mutate(weight_category = ifelse(pred_weight_g < 150, "lower", "upper"))

ggplot(sprat2, aes(x=pred_weight_g, y=log(ppmr)))+
  geom_point()+
  facet_wrap(~weight_category)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*sprat2$prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")

```

This does look like size has an effect on ppmr, but it still could be that
at these small sizes, the highest PPMRs are not acheivable for sampling 
constraints. 

```{r}

ggplot(sprat2)+
  geom_point(aes(x=log(ppmr), y=nprey_perpred, color=weight_category))

```

I think this point is an outlier and is why the PPMR has a wiggle.


```{r}

sprat2 <- sprat2%>%filter(nprey_perpred<5000)

ggplot(sprat2, aes(x=pred_weight_g, y=prey_ind_weight_g))+
  geom_point()+
  facet_wrap(~weight_category)+
  geom_smooth(method="gam", se=FALSE, aes(weight = nprey_perpred*prey_ind_weight_g^dig))+
  labs(title="logPPMR vs Predator Weight", x="Predator Weight (g)", y="logPPMR")

```

I am not sure why the geom_smooth moves down at 300 g, there shouldn't be
a high weighting value there.

So around the 300g / 400g mark, there are datapoints with high 
nprey_perpred (so high weightings) and also the prey weight is much higher.
I am not sure how to proceed.

I will just calculate it anyway.

 
```{r}

sprat$weight_numbers <- sprat$nprey_perpred
sprat$weight_biomass <- sprat$nprey_perpred*sprat$prey_ind_weight_g^dig

ggplot() +
  geom_density(data = sprat, aes(x = log(ppmr), weight = weight_biomass), color = "red") +
  geom_density(data = sprat, aes(x = log(ppmr), weight = weight_numbers), color = "blue") +
  labs(title = "Density Plot of log(ppmr) Weighted by Biomass and Numbers",
       x = "log(ppmr)",
       y = "Density") +
  theme_minimal()


```   

This looks like 2 mixture gaussains.


```{r}


library(mclust)

repeat_elements <- function(data, weights) {

    valid_indices <- !is.na(data) & !is.na(weights)
  data <- data[valid_indices]
  weights <- weights[valid_indices]
  
  final_vector <- c()

  for (i in seq_along(data)) {

    rounded_weight <- round(weights[i])

    repeated_values <- rep(data[i], times = rounded_weight)

    final_vector <- c(final_vector, repeated_values)
  }
  
  return(final_vector)
}

spratnu <- repeat_elements(log(sprat$ppmr), sprat$nprey_perpred)

gmm <- densityMclust(spratnu, G=1)

```

```{r}

dplot <- data.frame(x=gmm[["data"]], density=gmm[["density"]])


(numbfit <- ggplot() +
    geom_density(data=sprat, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
  geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Number Density Plot from Number Distribution"))

```
This is a good fit.

Now lets shift over.

```{r}

newspratdens <- gmm[["density"]]*exp(-dig*gmm[["data"]])
shifted_pdf_normalized <- newspratdens / sum(newspratdens) 

#making new dataframe
dplot <- data.frame(x=gmm[["data"]], density=shifted_pdf_normalized)

(numbfitbio <- ggplot() +
    geom_density(data=sprat, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
    geom_density(data=dplot, aes(x, weight=shifted_pdf_normalized), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

```

This isnt good

```{r}

spratnu <- repeat_elements(log(sprat$ppmr), sprat$nprey_perpred*sprat$prey_ind_weight_g^dig)
gmm <- densityMclust(spratnu, G=1)
dplot <- data.frame(x=gmm[["data"]], density=gmm[["density"]])

(biofit <- ggplot() +
    geom_density(data=sprat, aes(log(ppmr), weight=weight_biomass), fill="lightblue")+
  geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Diet Distribution"))

newspratdens <- gmm[["density"]]*exp(dig*gmm[["data"]])

shifted_pdf_normalized <- newspratdens / sum(newspratdens) 

dplot <- data.frame(x=gmm[["data"]], density=shifted_pdf_normalized)

(numbfitbio <- ggplot() +
    geom_density(data=sprat, aes(log(ppmr), weight=weight_numbers), fill="lightblue")+
    geom_density(data=dplot, aes(x, weight=shifted_pdf_normalized), fill="red", alpha=0.5)+
  #geom_line(data=dplot, aes(x = x, y = density), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Diet Density Plot from Number Distribution"))

sprat$l <- log(sprat$ppmr)
sprat <- sprat[!is.na(sprat$l),]
x_vals <- seq(min(sprat$l), max(sprat$l), length.out = 1000)

#I dont think I have done it right here, so I will do it in another way

shifted_fit <- gmm
shifted_fit[["parameters"]][["mean"]] <- shifted_fit[["parameters"]][["mean"]]+
  (1)*shifted_fit[["parameters"]][["variance"]][["sigmasq"]]

#generating the density values 
shifted_pdf <- sapply(x_vals, function(x) {
  sum(shifted_fit$parameters$pro * dnorm(x, mean = shifted_fit$parameters$mean, sd = sqrt(shifted_fit$parameters$variance$sigmasq)))
})

plot_data <- data.frame(x = x_vals, shifted_pdf = shifted_pdf)

(biofitnum <- ggplot() +
    geom_density(data=sprat, aes(log(sprat$ppmr), weight=weight_numbers), fill="lightblue")+
  geom_line(data=plot_data, aes(x = x_vals, y = shifted_pdf), color="red") +
  labs(x = "Values", y = "Density") +
  ggtitle("Number Density Plot from Diet Distribution"))


```

This doesnt work. Lets try the exponetial fit.


```{r}

stomach <- sprat
stomach$l <- log(stomach$ppmr)
stomach <- stomach[!is.na(stomach$l),]
stomach <- stomach %>% mutate(weight_numbers = nprey_perpred)

fl <- function(l, alpha, ll, ul, lr, ur) {
  dl <- ll - l
  dr <- l - lr
  fl_values <- exp(alpha * l) / (1 + exp(ul * dl)) / (1 + exp(ur * dr))
  
  # Debugging output
  if (any(!is.finite(fl_values))) {
    print("Non-finite fl values found")
    print(fl_values)
  }
  
  return(fl_values)
}

## Define the truncated exponential PDF with debugging
dtexp <- function(l, alpha, ll, ul, lr, ur) {
  fl_values <- fl(l, alpha, ll, ul, lr, ur)
  
  integral_result <- tryCatch(
    integrate(fl, 0, 30, alpha = alpha, ll = ll, ul = ul, lr = lr, ur = ur),
    error = function(e) {
      print("Integration failed")
     print(e)
      return(NULL)
    }
   )
   
   if (is.null(integral_result)) {
     return(rep(NA, length(l)))
   }
   
   d <- fl_values / integral_result$value
   
  # Debugging output
  if (any(!is.finite(d))) {
    print("Non-finite d values found")
    print(d)
  }
  
  return(d)
}

 #Define the MLE function with debugging
mle_texp <- function(df) {
  loglik <- function(alpha, ll, ul, lr, ur) {
    L <- dtexp(df$l, alpha, ll, ul, lr, ur)
    
    # Debugging output
    if (any(!is.finite(L) | L <= 0)) {
     print("Non-finite or non-positive L values found")
      print(which(!is.finite(L) | L <= 0))
      return(Inf)
    }
    
    -sum(log(L) * df$weight_numbers)
  }
  
  result <- tryCatch(
    mle2(loglik, start = list(
      alpha = 0.5,
      ll = min(df$l),
      lr = max(df$l),
      ul = 5,
      ur = 5
    ), method = "L-BFGS-B", control = list(maxit = 10000)),
    error = function(e) {
      print("MLE fitting failed")
      print(e)
      return(NULL)
    }
  )
  
  return(result)
}

est <- mle_texp(stomach)

biomassco <- est@coef

grid = seq(0, 30, length.out = 200)
#here, the alpha is meant to be -1, but I have to subtract 0.7 to make it work, so I am going to run the distribution again
#for the biomass, and see the difference
dist <- dtexp(grid, alpha = (biomassco[1]), ll = biomassco[2], ul = biomassco[3], 
              lr = biomassco[4], ur = biomassco[5])

dist <- data.frame(l=grid, Density=dist)

  ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = dist, color = "red")

```

Lets try to plot both.


```{r}

stomach <- stomach %>% mutate(weight_numbers = nprey_perpred * prey_ind_weight_g)
est <- mle_texp(stomach)
biomassestco <- est@coef

stomach <- stomach %>% mutate(weight_numbers = nprey_perpred)
est <- mle_texp(stomach)
numberestco <- est@coef

grid = seq(0, 30, length.out = 200)
dist <- dtexp(grid, alpha = (biomassestco[1]), ll = biomassestco[2], ul = biomassestco[3], lr = biomassestco[4], ur = biomassestco[5])
biomassdist <- data.frame(l=grid, Density=dist)
shiftdist <- dtexp(grid, alpha = (biomassestco[1]+1), ll = biomassestco[2], ul = biomassestco[3], lr = biomassestco[4], ur = biomassestco[5])
shiftbiomassdist <- data.frame(l=grid, Density=shiftdist)


dist <- dtexp(grid, alpha = (numberestco[1]), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
numberdist <- data.frame(l=grid, Density=dist)
shiftdist <- dtexp(grid, alpha = (numberestco[1]-1), ll = numberestco[2], ul = numberestco[3], lr = numberestco[4], ur = numberestco[5])
shiftnumberdist <- data.frame(l=grid, Density=shiftdist)
#now plot these two together

stomach <- stomach %>% mutate( biomass = nprey_perpred * prey_ind_weight_g)

ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = biomassdist, color = "red")+
  geom_line(aes(l, Density), data = shiftbiomassdist, color = "blue")+
  ggtitle("Fitted to Biomass, shift to number")

ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = numberdist, color = "red")+
  geom_line(aes(l, Density), data = shiftnumberdist, color = "blue")+
  ggtitle("Fitted to NUMBER, shift to Biomass")

```
Ok neither fits are good. Why does it shift so drastically?

Trying the shift in another way

```{r}

shiftbiomassdist$Density <- shiftbiomassdist$Density*exp(-shiftbiomassdist$l)
shiftbiomassdist$Density <- shiftbiomassdist$Density/sum(shiftbiomassdist$Density)

shiftnumberdist$Density <- shiftnumberdist$Density*exp(-shiftnumberdist$l)
shiftnumberdist$Density <- shiftnumberdist$Density/sum(shiftnumberdist$Density)


ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = biomassdist, color = "red")+
  geom_line(aes(l, Density), data = shiftbiomassdist, color = "blue")+
  ggtitle("Fitted to Biomass, shift to number")

ggplot(stomach) + 
  geom_density(aes(l, weight=weight_numbers))+
  geom_density(aes(l, weight=biomass))+
 xlab("Log of predator/prey mass ratio") + 
  geom_line(aes(l, Density), data = numberdist, color = "red")+
  geom_line(aes(l, Density), data = shiftnumberdist, color = "blue")+
  ggtitle("Fitted to NUMBER, shift to Biomass")


```

Still arent good fits. I think I am out of options.