---
title: "Stomach Data Exploration"
output: html_document
date: "2024-06-24"
---

## Compiling Data

Firstly, I am checking that PPMR is the same, irrespective of predator size and of region. So, I am 
going to include all DAPSTOM data, all anchovy and sardine data, and all ICES data. Then, I will go 
check that PPMR is equal across predator sizes.


```{r}
#packages
library(dplyr)
library(ggplot2)
library(tidyr)

#reading in the data

#ICES/DAPSTOM data
load("C:/Users/lucab/Downloads/stomach_dataset.Rdata")
#Anchovy and Sardine data
anc <- read.csv("C:/Users/lucab/Downloads/AnchovyAndSardine.csv")

#filtering out what I need to do calculations.
murray <- stom_df |>
  filter(!is.na(pred_weight_g),
         prey_ind_weight_g > 0,
         prey_count > 0) |>
  select(pred_species, pred_weight_g, prey_ind_weight_g, prey_count) |>
  group_by(pred_species) |> 
  filter(n() > 1000) |> 
  rename(w_prey = prey_ind_weight_g, w_pred = pred_weight_g, n_prey = prey_count) |>
  mutate(log_ppmr = log(w_pred / w_prey),
         weight_numbers = n_prey / sum(n_prey))

#reformating the Anc and Sard data to match

anc <- anc |>
  rename(pred_species = Species, w_prey = wprey, w_pred = wpredator, n_prey = Nprey) |>
  mutate(log_ppmr = log(0.1 / w_prey),
         weight_numbers = n_prey / sum(n_prey))

#bind. 
both <- bind_rows(murray, anc)

```

Now I have the data compiled and ready.
Will firstly plot the PPMR and predator mass.

```{r}
PPMRpred <- ggplot(both,
       aes(x = log(w_pred), y = log_ppmr)) + 
  geom_point() + geom_smooth(aes(weight = n_prey),colour = "red")+
  xlab("Log of predator mass [g]")+
  ylab("Log of predator/prey mass ratio")
```

```{r pressure, echo=FALSE}
plot(PPMRpred)
```

The PPMR changes across predator sizes, but lets change to include the biomass of prey
(of note later, at around 2.5, there is a straight line that have a very higher PPMR, 
will cover later on)


```{r}
ggplot(both,
  aes(x = log(w_pred), y = log_ppmr)) + 
  geom_point() + 
  geom_smooth(aes(weight = (n_prey * w_prey^(2 / 3))),colour = "red")+
  facet_wrap(vars(pred_species))+
  xlab("Log of predator mass [kg]")+
  ylab("Log of predator/prey mass ratio")+
  xlim(0,10)
```

It looks a lot better, and the PPMR doesn't change as much across predator sizes.
Next, I will plot the violin plot to see the change.

```{r}
#this next code is creating the breaks for the bins of equal datapoints
quantiles <- quantile(both$w_pred, probs = seq(0, 1, by = 0.1))
#then making the bins with these breaks.
both <- both %>%
  mutate(bin = cut(w_pred, breaks = quantiles, include.lowest = TRUE))

#now lets plot it.
ggplot(both, aes(bin, log_ppmr)) +
  geom_violin(aes(weight = n_prey * w_prey^(2/3)), draw_quantiles = 0.5) +
  xlab("Predator weight [g]") +
  ylab("Log of predator/prey mass ratio")
```
It is within the range 5-7.5 PPMR across predator weights, except for the smallest sizes and 
226-336. I would like to know what is different in 226-336. 

The next section I will investigate this.

The 226-336 bin range includes the line discussed prior. This doesn't look right,
so I am going to find this range of data, then remove it, and recalculate the 
violin plot. This hopefully will solve the issue.

```{r}
#subsetting to find the range 226 to 336
filtered_both <- both %>%
  filter(bin == "(226,336]")

#going to plot its range of ppmr
hist(filtered_both$log_ppmr)
```
```{r}
#I am next going to remove any that are above 12 from the violin dataset, and 
#replot it.

remove15 <- both%>%
  filter(!(bin == "(226,336]" & log_ppmr > 12))

add15 <- both%>%
  filter((bin == "(226,336]" & log_ppmr > 12))

ggplot(remove15, aes(bin, log_ppmr)) +
  geom_violin(aes(weight = n_prey * w_prey^(2/3)), draw_quantiles = 0.5) +
  xlab("Predator weight [g]") +
  ylab("Log of predator/prey mass ratio")

```
This looks a lot better now, but I'm not sure how scientific it is to remove datapoints that 
I dont like. Regardless, it still looked fishy that 226-336 was higher than all the rest. 
There is a slight deviation in 174-226, and looking at the PPMR figure (below), there is another straight line 
in the data that is greater than the rest, so it may be the same story here. It also appears that this straight line 
goes across half of the plot. (starts at approximately (-7.5, 1), finishes (2, 12))

```{r}
plot(PPMRpred)
```
I am going to try to identify the data that it came from

```{r}
#just going to vaguely define a line around it, then subset the data and 
#see what is similar.
line <- function(x) {
  slope <- (12 - 1) / (2 - (-7.5))
  intercept <- 1 - slope * (-7.5)
  return(slope * x + intercept)
}

within_20_percent <- function(x, y) {
  y_line <- line(x)
  return(abs(y - y_line) <= 0.2 * y_line)
}

subset_df <- both %>%
  filter(within_20_percent(log(w_pred), y = log_ppmr))
subset_df <- subset_df%>%
  filter(log(w_pred)<2.5)

ggplot(subset_df) +
  geom_point(aes(log(w_pred), log_ppmr), color = ifelse(subset_df$w_pred >= 0.174 & subset_df$w_pred <= 0.226, "red", "black"))

```
There are a few lines, in the data, so they can't have had very good scales. 
However, there isnt a line that goes across this range, but I can identify the data that 
is causing it to have a higher PPMR (between 2.25-2.35), and it does not appear to be a line,
but I want to find out what species it is. 

```{r}
OKAY WHERE AM I NOW
I DONT THINK THIS IS WORKING, THIS LINE OF INVESTIGATION, IT LOOKS GOOD ANYWAY, SO IT IS PROVEN REGIONALLY, 
NEXT SHOULD I AGGREGATE SPECIES AND DO THE SAME?
```

